Conditional resampling improves calibration \\ in single cell CRISPR screen analysis

### 2020-11-22 sceptre_paper/manuscript/manuscript_v3.tex

\addtocounter{page}{-1}
\thispagestyle{empty} 
\begin{figure}[h!]
	\includegraphics[width = \textwidth]{figures/Figure1/Figure1.png}
	\caption{\textbf{CRISPR screen analysis challenges can lead to false positives and false negatives.} \textbf{a}, QQ-plot of Gasperini et al. $p$-values for all gene-gRNA pairs involving either candidate enhancer or negative control gRNAs. Inflation in negative controls makes it harder to interpret associations between genes and candidate enhancers, motivating the empirical $p$-value correction. \textbf{b-c}, Sequencing depth (total mRNA UMIs per cell) impacts gRNA detection (b) and observed expression levels, and therefore acts as a confounder (c). This analysis challenge distinguishes CRISPR screens from traditional differential expression applications. \textbf{d-g}, Collapsing dispersion estimates to fitted mean-variance relationship (d) leads to over-correction for some genes (e) and under-correction for others (f, g). \textbf{d,} Dispersion estimation procedure employed leads to miscalibration for high-dispersion genes, which the empirical correction does not adequately correct for, as measured by KS test applied to empirical $p$-values per gene (point colors). \textbf{e,} Raw $p$-values already well-calibrated for LUC7L2 gene, so empirical correction unnecessarily shrinks the significance of the association with TSS-targeting gRNA, depicted by horizontal lines, by three orders of magnitude. \textbf{f,} Empirical correction not strong enough for HIST1H1D, which is among circled genes in panel d, which have an NTC-based miscalibration $p$-value smaller than the Bonferroni threshold. \textbf{g}, Under-correction leads to two potential false discoveries for HIST1H1D. Dashed horizontal line represents the multiple testing threshold.}
	\label{fig:analysis-challenges}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width = 0.75\textwidth]{figures/FigureS1/FigureS1.png}
	\caption{Sequencing depth (total mRNA UMIs per cell) impacts gRNA detection for Mosaic-seq data\cite{Xie2017}, as was demonstrated for Gasperini et al. data in Figure~\ref{fig:analysis-challenges}b.}
	\label{fig:mosaicseq}
\end{figure}

>>>>

\addtocounter{page}{-1}
\thispagestyle{empty} 
\begin{figure}[h!]
	\includegraphics[width = \textwidth]{figures/Figure1/Figure1.png}
	\caption{\textbf{CRISPR screen analysis challenges can lead to false positives and false negatives.} \textbf{a}, QQ-plot of Gasperini et al. $p$-values for all gene-gRNA pairs involving either candidate enhancer or negative control gRNAs. Inflation in negative controls makes it harder to interpret associations between genes and candidate enhancers, motivating the empirical $p$-value correction. \textbf{b-c}, Sequencing depth (total mRNA UMIs per cell) impacts gRNA detection (b) and observed expression levels, and therefore acts as a confounder (c). This analysis challenge distinguishes CRISPR screens from traditional differential expression applications. }
	\label{fig:analysis-challenges}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width = \textwidth]{figures/FigureS1/FigureS1.png}
	\caption{Gasperini et al.'s empirical correction is insufficient to correct for miscalibration. \textbf{a,} Dispersion estimation procedure employed leads to miscalibration for high-dispersion genes, which the empirical correction does not adequately correct for, as measured by KS test applied to empirical $p$-values per gene (point colors). \textbf{b,} Raw $p$-values already well-calibrated for LUC7L2 gene, so empirical correction unnecessarily shrinks the significance of the association with TSS-targeting gRNA, depicted by horizontal lines, by three orders of magnitude. \textbf{c,} Empirical correction not strong enough for HIST1H1D, which is among circled genes in panel a, which have an NTC-based miscalibration $p$-value smaller than the Bonferroni threshold. \textbf{d}, Under-correction leads to two potential false discoveries for HIST1H1D. Dashed horizontal line represents the multiple testing threshold.}
	\label{fig:mosaicseq}
\end{figure}
